---
name: Doyeon (Doy)
surname: Kim
position: "Quantitative Researcher · Program Evaluation · Educational Technology"
address: "Madison, WI"
email: "doy.kim@wisc.edu"
linkedin: "doy-kim"
github: "doy-kim-research"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tidyverse)
library(glue)
library(readr)

split_semi <- function(x) {
  map(x, ~ {
    if (is.na(.x) || .x == "") return(NULL)
    str_split(.x, ";\\s*")[[1]]
  })
}
```

# Summary

Learning scientist and quantitative researcher with a decade of experience designing and evaluating education programs and technologies in authentic K--12 and postsecondary settings. Currently a Doctoral Research Intern in WestEd's Center for Teaching and Learning, building and maintaining end-to-end data pipelines and evaluating educational technology interventions through randomized and quasi-experimental designs. Background spans rigorous quantitative methods (experimental design, structural equation modeling, causal inference), mixed-methods data collection, and technical reporting for diverse audiences. Former certified secondary mathematics teacher and developer of mathematics professional development for over 7,000 in-service teachers.

# Relevant Experience

```{r experience}
experience  <- read_csv("data/resume_experience.csv",         show_col_types = FALSE)
exp_details <- read_csv("data/resume_experience_details.csv", show_col_types = FALSE)

detail_lists <- exp_details %>%
  arrange(position_id, order) %>%
  group_by(position_id) %>%
  summarise(why = list(detail), .groups = "drop")

experience %>%
  left_join(detail_lists, by = c("id" = "position_id")) %>%
  detailed_entries(
    what  = role,
    when  = when,
    with  = organization,
    where = location,
    why   = why
  )
```

# Skills

```{r skills}
read_csv("data/resume_skills.csv", show_col_types = FALSE) %>%
  group_by(category) %>%
  summarise(skills_list = paste(skill, collapse = " · "), .groups = "drop") %>%
  brief_entries(
    what = skills_list,
    with = category
  )
```

# Education

```{r education}
read_csv("data/education.csv", show_col_types = FALSE) %>%
  mutate(why = split_semi(details)) %>%
  detailed_entries(
    what  = degree,
    when  = when,
    with  = institution,
    where = location,
    why   = why
  )
```

# Selected Publications

```{r publications}
bibliography_entries("data/resume_publications.bib") %>%
  arrange(desc(issued))
```
